A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-10 main.tex
Anonymize by using \ifnotanonymous.
Add two papers into the section of reference.

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bcprules, proof}
\usepackage{fancybox}
\usepackage{mathtools}
\usepackage{float}
\usepackage{xparse}
\usepackage{lscape}
\usepackage{mdframed}
\usepackage{xspace}

@@

\begin{document}
%
\title{A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
    Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{A. Kawata, A. Igarashi}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
    \email{akira@fos.kuis.kyoto-u.ac.jp} \and
    \email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}

@@

    \keywords{Multistage programming \and Dependent type}
\end{abstract}

@@

\begin{align*}
	\textrm{Type variables}  &  &                          & X,Y,Z                                                                             \\
	\textrm{Constants}       &  &                          & c                                                                                 \\
	\textrm{Variables}       &  &                          & x,y,z                                                                             \\
	\textrm{Stage variables} &  &                          & \alpha,\beta,\gamma                                                               \\
	\textrm{Stage}           &  &                          & A,B,C                                                                             \\
	\textrm{Kinds}           &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
	\textrm{Types}           &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
	\textrm{Terms}           &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
	\mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                                                                  \\ 
	\textrm{Signature}       &  & \Sigma                   & ::= \phi \mid X::K \mid c:\tau                                                    \\
	\textrm{Contexts}        &  & \Gamma                   & ::= \phi \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{FV}(\tau))                         \\
\end{align*}

@@

Applications of dependent types for real problems were also researched.
In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
and succeeded in reducing the bounds checking of arrays.
Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.

@@

@@

\begin{itemize}
	\item On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}

	      CSPも入りました
	\item Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
	\item MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
	\item Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
	\item A Logical Foundation for Environment Classifiers\cite{Tsukada}
	\item Environment classifiers\cite{taha2003environment}
	\item A framework for defining logics\cite{harper1993framework}

	      $\Sigma$ の使い方を確認した
	\item The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
	\item Refined Environment Classifiers\cite{kiselyov2016refined}
	\item Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
	\item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
	\item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
	\item Dependent types in practical programming\cite{xi1999dependent}

@@

	\item A dependently typed assembly language\cite{xi2001dependently}

	      DTALの定義と制約solverを用いた型検査の定義
	\item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
	\item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
	\item \red{Run-time bytecode specialization}\cite{masuhara2001run}
	\item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
	\item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
	\item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}

\end{itemize}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\newif\ifnotanonymous \notanonymousfalse
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bcprules, proof}
\usepackage{fancybox}
\usepackage{mathtools}
\usepackage{float}
\usepackage{xparse}
\usepackage{lscape}
\usepackage{mdframed}
\usepackage{xspace}

@@

\begin{document}
%
\title{A Dependently Typed Multi-Stage Calculus%
  \ifnotanonymous\thanks{Supported by organization x.}\fi
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\ifnotanonymous
\author{Akira Kawata\inst{1} \and
    Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
% %
\authorrunning{A. Kawata, A. Igarashi}
% % First names are abbreviated in the running head.
% % If there are more than two authors, 'et al.' is used.
% %
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
    \email{akira@fos.kuis.kyoto-u.ac.jp} \and
    \email{igarashi@kuis.kyoto-u.ac.jp}
}
\fi
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}

@@

    \keywords{multi-stage programming, cross-stage persistence, dependent types}
\end{abstract}

@@

\begin{align*}
	\textrm{Type variables}  &  &                          & X,Y,Z                                                                             \\
	\textrm{Constants}       &  &                          & c                                                                                 \\
	\textrm{Variables}       &  &                          & x,y,z                                                                             \\
	\textrm{Stage variables} &  &                          & \alpha,\beta,\gamma                                                               \\
	\textrm{Stage}           &  &                          & A,B,C                                                                             \\
	\textrm{Kinds}           &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
	\textrm{Types}           &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
	\textrm{Terms}           &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
	\mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                                                                  \\ 
	\textrm{Signature}       &  & \Sigma                   & ::= \emptyset \mid X::K \mid c:\tau                                                    \\
	\textrm{Contexts}        &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G))                         \\
\end{align*}

@@

Applications of dependent types for real problems were also researched.
In Xi and Pfenning\cite{Xi98}, they extended SML with restricted dependent types
and succeeded in reducing the bounds checking of arrays.
In Xi and Robert\cite{xi2001dependently}, they design a type system for an assembly language and
it is useful for spped up.
Xi also gave dead code elimination and loop unrolling as examples of dependent types application in \cite{xi1999dependent}.

@@

% 他段階計算の機能拡張

Combination of multistage programming and another programming feature has been studied.
Oleg, Kameyama, and Sudo\cite{kiselyov2016refined} designed a type sysytem for multistage programming with mutable cells and
Oishi and Kameyama\cite{oishi2017staging} extended a multistage calculus so that it can handle control operators such as shift and reset.

@@

\begin{enumerate}
	\item Done: On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}

	      CSPも入りました
	\item Done: Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
	\item Done: MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
	\item Done: Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
	\item Done: A Logical Foundation for Environment Classifiers\cite{Tsukada}
	\item Done: Environment classifiers\cite{taha2003environment}
	\item Done: A framework for defining logics\cite{harper1993framework}

	      $\Sigma$ の使い方を確認した
	\item Done: The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
	\item Done: Dependent types in practical programming\cite{xi1999dependent}

@@

	\item Done: A dependently typed assembly language\cite{xi2001dependently}

		  DTALの定義と制約solverを用いた型検査の定義
	\item Done: Refined Environment Classifiers\cite{kiselyov2016refined}
	\item Done: Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
	\item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
	\item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
	\item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
	\item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
	\item \red{Run-time bytecode specialization}\cite{masuhara2001run}
	\item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
	\item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
	\item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}

\end{enumerate}
